Studying public transit API query logs\\ to get an indication of travel flows

### 2016-01-07 paper.tex

%\todo{Rework introduction at the end}

@@

Getting indications of people flows through public transit networks is a challenge.
Today, the Belgian railway company (SNCB) takes samples, manually, of people getting on and off trains in stations. 
To date, this is still the SNCB's only source to determine people flows through their network\footnote{\url{http://www.belgianrail.be/nl/corporate/in-de-kijker/comptages_voyageurs_2014.aspx}}.
Also within other transit systems the data is tedious to get, certainly when passengers do not have to check-in and check-out.

\emph{Can we get an indication of these transit flows by studying the query logs of Web-services?}

In this paper, we give a small overview of related work to gather data for flow analysis.
We study these query logs by creating a couple of visualizations which illustrate a couple of patterns.
Next, we study the iRail query logs to find out whether we can find interesting patterns.
Finally, we look at public transit data is being published, and how we would be able to get a better .

>>>>

%\todo{Rework introduction at the end}
Today, the Belgian railway company (SNCB) takes manual samples of people getting on and off trains in stations. 
To date, this is still the SNCB's only source to determine people flows through their network\footnote{\url{http://www.belgianrail.be/nl/corporate/in-de-kijker/comptages_voyageurs_2014.aspx}}.
Also within other transit systems the data is tedious to get, certainly when passengers do not have to check-in and check-out.
Nonetheless, indications of how people move within your transit network is of uttermost importance for, amongst others, taking demand-driven policy decisions concerning mobility.

@@

Getting indications of people flows through public transit networks is a challenge. 
Yet, \emph{can we not get an indication of these transit flows by studying the query logs of Web-services?}

In this paper, we give a small overview of related work to gather data for flow analysis.
Next, we introduce the iRail query logs, which we study by the means of visualizations.
Finally, we look at public transit data is being published, and how we would be able to get a better indication of travel flows than just mere query logs.
